Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-19 paper/current/main.tex
data availabiltiy

%
% Supporting Information
% 
\subsection*{Additional Information}
Supplementary Information is available for this paper.
Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn.
Reprints and permissions information is available at www.nature.com/reprints

\subsection*{Data Availability}
The U.S. airline itinerary dataset can be found at XYZ. 
The South Korean accommodation reservation dataset can be found at XYZ.
Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
however, we have made available all metadata and trained neural embeddings available at XYZ.

>>>>

%
% Supporting Information
% 
\subsection*{Additional Information}
Supplementary Information is available for this paper.
Correspondence and requests for materials should be addressed to Dr. Staša Milojević and Dr. Yong-Yeol Ahn.
Reprints and permissions information is available at 
\url{www.nature.com/reprints}.

\subsection*{Data Availability}
The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
In case of the South Korean accommodation reservation dataset, due to the nature of the dataset, participants of this study did not agree for their data to be shared publicly.
Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
however, we have made available all metadata and trained neural embeddings available at XYZ.
